Testing Statistical Graphics

### 2022-06-27 index.qmd
rephrasing

Visual assessment is key, but narrowing the parameter space down to something that can be statistically determined is useful for providing a sort of numerical magnitude of difficulty assessment. 
If using model based sampling methods, it is important to iteratively assess the sampling procedure through simulation: Start with a sampling method and define a parameter space that is appropriate for the model, and then simulate many data sets from each possible parameter combinations using a grid search.
When sampling from a large data set, it is still important to assess the sample size and any potential stratification methods employed in order to ensure that the visual effect is represented.

>>>>

Visual assessment is key, but narrowing the parameter space down to something that can be statistically determined is useful for providing a sort of numerical summary estimate of potential visual difficulty. 
If using model based sampling methods, it is important to iteratively assess the sampling procedure through simulation: Start with a sampling method and define a parameter space that is appropriate for the model, and then simulate many data sets from each possible parameter combinations using a grid search.
When sampling from a large data set, it is still important to assess the sample size and any potential stratification methods employed in order to ensure that the visual effect is represented.
